\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{array}
\usepackage{tikz}
\usepackage{hyperref}
\pagestyle{fancy}
\fancyhf{}
 
\def\ci#1{\textcircled{\resizebox{.5em}{!}{#1}}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection
{Emanuel}
{Muñoz}
{\href{mailto:emanuel.munoz@utec.edu.pe}{\textit{emanuel.munoz@utec.edu.pe}}} %3
{\href{https://github.com/EmanuelSamir}{\ci{\faGithub}}} %4
{\href{https://www.linkedin.com/in/EmanuelSamirMP/en}{\ci{\faLinkedin}}} % 5
{\href{https://scholar.google.com/citations?user=KjixlLsAAAAJ&hl=es&oi=ao}{\ci{\faGraduationCap}}} %6
{\href{https://api.whatsapp.com/send/?phone=51947263845}{\ci{\faWhatsapp}}} % 7
{Python, Matlab, C++} %8
{Torch, Scikit, TF, OpenCV} %9
%10

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\begin{minipage}[t]{0.95\linewidth} 
\textbf{Senior Peruvian student} of Electrical Engineering at UTEC. Interested in \textbf{AI,  Computer Vision}, and Robotics for global or social issues. Worked on projects related to surgical robotics, autonomous vehicles, machine learning, and control with \href{https://scholar.google.com/citations?user=KjixlLsAAAAJ&hl=es&oi=ao}{\textbf{six indexed publications}}. Collaborated with material science project at \textbf{Yale University}. Accepted into selective AI and Robotics  
\href{https://riss.ri.cmu.edu/}{\textbf{RISS program}} at \textbf{Carnegie Mellon University}. Currently, I am working on my thesis project based on \textbf{Deep Reinforcement Learning} applied on mobile robots for exploration tasks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\runsubsection{\href{https://www.utec.edu.pe/en/}{Universidad de Ingeniería y Tecnología - UTEC}}
\descript{| Electrical Engineering}
\location{March 2016 - Expected December 2021 | Lima, Perú}
\textbf{Upper Top-Fifth} | Senior Undergraduate Student |
\textbf{Awarded with Full Academic Scholarship} \\
\textbf{Cum. GPA: 4.00} | GPA in Peruvian scale: 15.86/20.00 | \textbf{Thesis project:} AI-curiosity-driven exploration in mobile robots.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
%\runsubsection{\href{https://riss.ri.cmu.edu/}{Carnegie Mellon University - Robotics Institute}}
%\descript{| Incoming internship }
%\location{June 2021 - August 2021| Remote}
%\begin{tightemize}
%\item  %\end{tightemize}

\runsubsection{\href{http://www.utecgo.edu.pe/sites/default/files/field/PPT Research v.8.pdf\#page=127}{UTEC - CONCYTEC}}
\descript{| Robotics Research Assistant }
\location{ March 2020 – Currently | Lima, Perú}
\begin{tightemize}
    \item Collaborated in a \textbf{two-year government-funded project} to implement a nonlinear controller in a surgical robot platform based on haptic control. | Published \href{https://scholar.google.com/citations?user=KjixlLsAAAAJ&hl=es&oi=ao}{\textbf{two indexed  papers}}, one pending. | \textbf{Tech:}\tech{ROS, Python, Gazebo.}
    \item Implemented a \textbf{hybrid learning controller} for torque-position transformation in manipulator robots
    \item Designed and implemented a camera framework for feedback sensing using \textbf{computer vision} and filtering techniques.
\end{tightemize}

\sectionsep
\runsubsection{Yale University - \href{https://seas.yale.edu/faculty-research/faculty-directory/jan-schroers}{Schroers Lab} }
\descript{| Research Assistant}
\location{Jan - March 2020 | New Haven, CT, US}
\begin{tightemize}
    \item Sponsored by \href{https://www.repuprogram.org/nanorepu}{Research Experience for Peruvian Undergraduates} | Supervised by \href{https://seas.yale.edu/faculty-research/faculty-directory/jan-schroers}{Jan Schroers} and Sungwoo Sohn.
    \item Designed and developed two new alloys with potential mechanical properties for industrial applications.
\end{tightemize}

\sectionsep
\runsubsection{\lowercase{\href{https://www.isarep.com.pe/SitePages/Home.aspx?lang=en}}{ISA REP}}
\descript{| Digital Image Processing Intern}
\location{Jun – Dec 2019 | Lima, Perú}
\begin{tightemize}
    \item Designed and developed two methods for corrosion detection based on \textbf{computer vision and AI} for decision making.
    \item Launched the first phase of automatic supervision of +1000 km powerlines using drones and machine learning.
    \item Developed framework for semantic labeling, classifier training, and GUI prototype. | \textbf{Tech:}\tech{scikit, Keras, OpenCV, PyQT}  
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\section{Projects}
\project{Minsky | \href{https://github.com/minskylab}{\faGithub} \href{https://minsky.cc/https://minsky.cc/}{\faLink}}
\begin{tightemize}
    \item Collaborated in open source web-based projects for Minsky company.
    \item Participated in COVID-19 oriented hackathons proposing web-based solutions.
\end{tightemize}

\project{Navigation robotics with AI | \href{https://github.com/EmanuelSamir/2d-navigation-drl}{\faGithub}
\href{https://github.com/EmanuelSamir/2d-navigation-drl/blob/main/_EEML__Extended_Abstract.pdf}{\faPaperclip}}
\begin{tightemize}
    \item Developed an actor-critic agent applied on a mobile robot for exploration and navigation tasks. \textbf{Tech:}\tech{Gym, Torch}   
\end{tightemize}

\project{Image Enhancer | \href{https://github.com/EmanuelSamir/DIP_project_Testing}{\faGithub}}
\begin{tightemize}
    \item Built a model architecture to automate beauty-enhancing of photos using image manipulation. \textbf{Tech:}\tech{TF, scikit}.
\end{tightemize}
\project{Autonomous Mobile Robotics | \href{https://github.com/EmanuelSamir/201_dev_rndlocalizer}{\faGithub}} 
\begin{tightemize}
    \item Designed and implemented algorithms for \textbf{autonomous} motion planning and exploration on mobile robots in real and simulated environments. | \textbf{Tech:}\tech{ROS, Gazebo} 
    \item Built complete frameworks for mobile robotic applications and \href{https://scholar.google.com/citations?user=KjixlLsAAAAJ&hl=es&oi=ao}{\textbf{published four papers}} showing results. 
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Additional Information} 
\begin{tabular}{rll}
2021	     & Selected for research internship at \href{https://riss.ri.cmu.edu/}{ \textbf{Carnegie Mellon’s Robotics Institute Summer Scholars (RISS) program}}  \\
2021	     & Accepted to participate on \href{https://www.yorku.ca/cvr/summer-school/}{\textbf{VISTA Vision Science and AI Summer School}} at \textbf{York University} \\
2020	     & Selected out of 300+ students by \href{https://www.repuprogram.org/}{\textbf{REPU}} to work on nano science research internship at \textbf{Yale University}  \\
2019	     & Accepted with financial support in the \href{http://robotvision2019.amtc.cl/}{\textbf{International Summer School on Deep Learning for Robot Vision}} at Chile \\
\end{tabular}

\section{Interests}
\interest{Deep Learning, decentralized tech, science divulgation, start-up, table tennis, Sherlock Adventures, cooking}
\end{minipage} 
\end{document}  \documentclass[]{article}
